\bfseries\large Phosphatidylinositol 4,5-bisphosphate regulates cilium transition zone maturation in \textit{Drosophila melanogaster}

### 2018-02-11 latex/paper.tex
updated

% title font size
\titleformat*{\section}{\normalsize\bfseries}
\titleformat*{\subsection}{\normalsize\bfseries}

@@

% new commands
\newcommand{\PIP}{PIP\textsubscript{2}}
\newcommand{\sigd}{$\beta$\textit{2tub}-SigD}
\newcommand{\sktl}{\textit{sktl}}
\renewcommand*{\Affilfont}{\footnotesize \normalfont}
\renewcommand*{\Authfont}{\normalsize}

\title{\bfseries\large Phosphatidylinositol 4,5-bisphosphate regulates cilium transition zone maturation in Drosophila}
\author[1,2]{Alind Gupta \thanks{\url{alind.gupta@mail.utoronto.ca}}}
\author[1,2]{Julie A. Brill \thanks{\url{julie.brill@sickkids.ca} (Corresponding author)}}
\affil[1]{Department of Molecular Genetics, University of Toronto, Toronto, ON M5S 1A8, Canada}
\affil[2]{Program in Cell Biology, Hospital for Sick Children, Toronto, ON M5G 1X8, Canada}
\date{}

\begin{document}
\maketitle
\raggedright
\begin{abstract}
  \vspace*{-0.7em}
  Cilia are sensory organelles that are important for human development
  and physiology.
  A large number of genetic disorders affecting cilia are associated with
  mutations in proteins that localize to the transition zone (TZ),
  a structure at the base of cilia required for ciliogenesis and
  regulation of trafficking in and out of the cilium.
  Here, we report that the membrane lipid phosphatidylinositol
  4,5-bisphosphate(\PIP{}) is essential for proper maturation and function
  of TZs in the male \textit{Drosophila melanogaster} germline.
  Reduction of cellular \PIP{} levels by expression of the
  \textit{Salmonella} phosphoinositide phosphatase SigD or mutation of
  the type I phosphatidylinositol phosphate kinase Skittles (Sktl)
  induces hyperelongation of TZs following their docking at the plasma
  membrane.
  We provide evidence showing that these hyperelongated TZs are functionally
  defective, and that the Exo84 mutant \textit{onion rings} decouples the
  transition zone hyperelongation from the role for \PIP{} in cilium-membrane
  tethering.
  Our observations reveals a requirement for \PIP{} at the base of cilia
  in regulating TZ length and function.
\end{abstract}

\section{Introduction}
Cilia are sensory organelles present on almost all cells in the human body
\citep{satir2010primary}.
They function primarily by providing sensory inputs to cells, but can
also function as motile propellers in certain cells
\citep{bloodgood2010sensory}.
Consistent with their pervasiveness and importance in cell signalling,
defects in cilium formation are associated with various genetic disorders
known collectively as ciliopathies, which can manifest as
neurological disorders \citep{valente2014primary},
skeletal abnormalities \citep{hammarsjo2017novel, waters2011ciliopathies}
and infertility \citep{inaba2016sperm}.

A large number of ciliopathies are linked to mutations in proteins that
localize to the cilium transition zone (referred to herein as TZ).
The TZ is the proximal-most compartment of the cilium which
acts as a diffusion barrier that regulates the
bi-directional transport of protein and lipid cargo at the base of the cilium,
and is essential for cilium formation and function in cell signalling.
The conserved TZ protein CEP290, for example, is mutated in at least
five distinct ciliopathies, and is essential for cilium formation in both humans
and Drosophila.
Although the composition of TZs is well understood, processes underlying
transition zone maturation and cell membrane anchoring are not as well-studied.
In particular, why mutations in the same TZ protein can give rise to a plethora
of phenotypic outputs is less understood, and may point at modifier mutations
or mutations that are not as severe as to entirely abolish ciliogenesis.

In the Drosophila male germline, nascent TZs first assemble on basal bodies
during early pre-meiotic G2 phase (spermatocytes), anchor directly to the plasma membrane.
This is followed by establishment of cilium-membrane connections and a
ciliary membrane that persists during meiosis \citep{riparbelli2012assembly}
through a poorly understood mechanism
involving microtubule rearrangements \citep{gottardo2013cilium}.
Ciliogenesis begins with the assembly of TZ proteins at the tips of
the nascent basal body.
This is followed by the anchoring of the TZ to the membrane and
establishment of a compartmentalized space bounded by the ciliary membrane
and the TZ.
TZ maturation has been described in
\textit{Paramecium} \citep{aubusson2015transition}
\textit{Caenorrhabditis elegans} \citep{serwas2017centrioles} and
\textit{D. melanogaster} \citep{gottardo2013cilium}
and involves TZ elongation.
Possibly, this is similar to the initial steps of TZ assembly and reorganization
in well-studied vertebrate cilia.

Here, we show that the lipid phosphatidylinositol 4,5-bisphosphate (\PIP{})
is essential for proper TZ maturation in developing \textit{Drosophila melanogaster}
male germ cells.
Reduction of cellular \PIP{} by expression of the bacterial PIP phosphatase SigD
or by inactivation of the PIP 5-kinase Skittles (Sktl) that localizes to cilia
induces longer than normal TZs.
These hyperelongated TZs show hallmarks of aberrant function similar to those
found in previously studied TZ mutants, including loss of cilium-membrane associations.
We also find that the \textit{onion rings} allele of the
ciliopathy-associated \textit{EXOC8} gene encoding the human Exo84
decouples TZ hyperelongation from loss of cilium-membrane contacts.
Our results suggest that the plasma membrane lipid \PIP{} regulates TZ length,
maturation and function, acting to support ciliogenesis.

\section{Results}

\subsection{\PIP{} is essential for transition zone maturation}
To investigate whether reduction of cellular \PIP{} affects ciliogenesis in the
Drosophila male germline,
we used transgenic flies expressing the Salmonella phosphoinositide phosphatase SigD
under $\beta$2-tubulin promoter (referred to herein as \sigd{}),
which is uniquely expressed in spermatocytes
\citep{wei2008depletion, fabian2010phosphatidylinositol}.
We previously showed that expression of this construct
induced male sterility due in part to defects in flagellar biosynthesis \citep{wei2008depletion}.
We examined the localization of fluorescently-labelled centriolar/basal body protein
Ana1 (Cep295) \citep{goshima2007genes, blachon2009proximal}
and the TZ protein Cep290 \citep{basiri2014migrating}
in wild-type control and \sigd{} spermatocytes.
As shown in Figure 1A, nascent TZs marked with Cep290-GFP assemble normally in \sigd{} cells
but grow to much longer lengths compared to wild-type control cells.
TZ hyperelongation was a highly penetrant phenotype (\textgreater 90\%)
and showed high intra-cyst correlation.
This phenotype was not specific to Cep290;
all TZ markers examined showed hyperelongation, including
acetylated tubulin \citep{gottardo2013cilium},
Chibby \citep{enjolras2012drosophila} and
MKS \citep{slaats2015mks1, vieillard2016transition} proteins (Figure 1).
Hyperelongated transition zones persisted through meiosis.
Despite TZ hyperlongation, however, axonemes were able to elongate post-meiosis (Figure 1).
As we showed previously, the ultrastructure of these axonemes was frequently aberrant,
either lacking symmetry completely or containing triplet microtubules instead of doublets
\citep{wei2008depletion}.

\subsection{The type I PIP kinase Skittles localizes to centrioles and regulates TZ length}
Although numerous studies have shown that \PIP{} is the major substrate for SigD
when expressed in eukaryotic cells
\citep{terebiznik2002elimination, zhou2001salmonella, sengupta2013depletion},
SigD can dephosphorylate other PIPs \textit{in vitro}
\citep{norris1998sopb}.
To address whether TZ hyperelongation observed in \sigd{} represented
a physiologically relevant phenotype in response to decreased \PIP{},
we attempted to rescue it by
co-expressing fluorescently-tagged full-length Skittles (Sktl) with SigD
under the same promoter.
We found that Sktl expression was able to suppress TZ elongation in a cilium-autonomous
manner (Figure 2).
We also found that \textit{sktl} clones showed penetrant TZ hyperelongation when
marked with Unc-GFP, a ciliary marker \citep{baker2004mechanosensory}.

Since Sktl expression lead to cilium-autonomous rescue,
we investigated whether Sktl could localize to centrioles or cilia in the Drosophila germline.
Similar to the human PIPKI$\gamma$ isoform \citep{xu2014pipkigamma},
we found that Skittles localizes to basal bodies in the Drosophila male germline.
As shown in Figure 2, Drosophila PIP5Ks arose from the recent duplication of
the ancestral PIP5K gene, and are not orthologous to specific vertebrate PIP5K isoforms.
Skittles has diverged more than the paralogous PIP5K59B gene, and seems
to be functionally related to PIPKI$\gamma$ in its roles at cilia.
However, unlike the human PIPKI$\gamma$, which functions to license TZ assembly
by promoting CP110 uncapping from basal bodies \citep{xu2016phosphatidylinositol},
our results suggest that Skittles functions in
regulating TZ length in the Drosophila male germline
but is dispensable for its assembly.
The localization of Cp110 is unaffected in \sigd{} (supplementary figure 1).

@@

\section{Discussion}

Cilia are essential for proper human development, and their disruption
can cause genetic disorders which display severity ranging from congenital
lethality to adult onset.
A large number of ciliopathies are associated with genes that encode for
proteins that function at the cilium transition zone (TZ).
Often, a single gene is linked to multiple ciliopathies with variable phenotypes
and severities.
For example, the conserved TZ protein CEP290 is linked to at least six different
cilium-associated disorders, suggesting that many of these encode for mutant proteins
that are hypomorphic in nature whose function may
be affected by modifier mutations and genetic environment.
Animal models with mild perturbations of TZ function may therefore provide
insight on intermediate phenotypes associated with human disease.
Here, we found that reduced levels of the membrane lipid \PIP{},
which is known to be enriched at the base of cilia,
affects TZ maturation, but not assembly,
leading to hyperelongated TZs that show signs of functional defects, and
may represent one such modifier for TZ function.

In the Drosophila male germline, TZ maturation follows the initial
assembly of TZ proteins on the nascent basal body in the cytoplasm
followed by anchoring at the plasma membrane.
TZ maturation involves microtubule rearrangements and TZ elongation,
which leads to cilium-membrane attachment.
Loss of \PIP{}, a membrane lipid largely at the plasma membrane,
disrupts this process.
It causes excessive lengthening of the TZ,
and disrupts membrane-cilium connections.

@@

\section{Methods}
\subsection{Transgenic flies}
Drosophila stocks were cultured on cornmeal molasses agar medium at 25$^{\circ}$C
and 50\% humidity.
Stocks expressing $\beta$\textit{2tub}::SigD and $\beta$\textit{2tub}::YFP-Sktl
were described previously \citep{wei2008depletion, fabian2010phosphatidylinositol}.
Ana1-tdTomato (chromosome 2) and Cep290-GFP (chromosome 3) were provided
by T. Avidor-Reiss \citep{basiri2014migrating}.
Unc-GFP was originally provided by M. Kernan \citep{baker2004mechanosensory}.
Stocks expressing GFP-tagged Chibby, B9d1, B9d2, Cc2d2a and Mks1 were generously
provided by B. Durand \citep{enjolras2012drosophila, vieillard2016transition}.
The \textit{onr} mutant was described previously \citep{giansanti2015exocyst}.
Stocks for generating \textit{sktl}\textsuperscript{2.3} clones were originally provided by
A. Guichet \citep{gervais2008pip5k}.
\textit{w}\textsuperscript{1118} was used as the wild-type control.

\subsection{Antibodies}
The following primary antibodies were used for immunofluorescence
at the indicated concentrations - 
rabbit $\alpha$-Tulp (gift from W. McGinnis \citep{ronshaugen2002structure}), 1:500; 
chicken $\alpha$-GFP IgY (abcam) 1:1000;
rat $\alpha$-RFP IgG (5F8, ChromoTek), 1:1000;
rabbit $\alpha$-Sktl (courtesy of P. Raghu), 1:500;
Secondary antibodies were Alexa 488- and Alexa 568-conjugated
$\alpha$-mouse, $\alpha$-rabbit and $\alpha$-chicken
IgG (Molecular Probes) at 1:1000.
DAPI was used to label chromatin at 1:1000.

@@

For immunochemistry, testes were dissected in PBS,
transferred to a polylysine-coated gladd slide in a drop of PBS,
ruptured with a needle, squashed and frozen in liquid nitrogen for 5 minutes.
The slides were transferred to ice-cold methanol for 5-10 minutes.
For staining with the $\alpha$-skittles antibody, pre-fixation in methanol
was omitted to preserve cellular membranes.
Samples were fixed in 4\% paraformaldehyde in PBS,
permeabilized and blocked in PBS with 0.1\% Triton-X and 0.3\% bovine
serum albumin and incubated with primary antibodies overnight at 4$^{\circ}$C.
followed by three 5-minute washes with PBS and 1 hour incubation
with secondary antibodies and three 5-minute washes with PBS.
Samples were mounted in Dako (Agilent) and imaged with Leica widefield microscope
or Nikon A1R scanning confocal microscope (SickKids imaging facility).

\subsection{Statistical methods}
Statistical analysis and graphing was performed using R.
A Gaussian jitter was applied when plotting
results in Figures 1 and 2,
but raw data was used for all analysis.
Statistical tests for ``absence of phenotype'' were computed under a
hypothesis assuming binomial likelihood (i.e. assuming a fixed probability of the
phenotype occurring).
All $t$-tests were unpaired and two-sided.
A significance level of 0.01 was fixed \textit{a priori} for all classical analysis.
Bayesian analysis was performed in Stan.
All raw data and code for analysis and plotting can be found online
at \url{http://www.github.com/alindgupta/germline-paper/}.

\subsection{Phylogenetic analysis}
Candidate orthologs of \textit{sktl} or \textit{pip5k59b} were queried from Inparanoid and FlyBase.
Poorly annotated protein sequences were manually curated to ensure
these represented type I phosphatidylinositol phosphate
kinases using reciprocal BLAST search.
Phylogeny.fr (\url{http://www.phylogeny.fr}) was used for
phylogenetic reconstruction with T-Coffee for multiple alignment
and MrBayes for tree construction.
The output was converted to a vector image in Illustrator
and colours were added for the purposes of illustration.

\section{Author contributions}
A.G. and J.A.B. conceived the project.
A.G. performed all the experiments and wrote the manuscript.
J.A.B. supervised the project.

\section{Acknowledgements}
We thank Brian Ciruna for his input on the project
and B. Durand for graciously providing unpublished fly stocks.

>>>>

% title font size
\titleformat*{\section}{\large\bfseries}
\titleformat*{\subsection}{\normalsize\bfseries}

@@

% new commands
\newcommand{\PIP}{PIP\textsubscript{2}}
\newcommand{\sigd}{$\beta$\textit{2t}-SigD}
\newcommand{\sktl}{\textit{sktl}}
\renewcommand*{\Affilfont}{\footnotesize \normalfont}
\renewcommand*{\Authfont}{\normalsize}

\title{\bfseries\large Phosphatidylinositol 4,5-bisphosphate regulates cilium transition zone maturation in \textit{Drosophila melanogaster}}
\author[1,2]{Alind Gupta \thanks{\url{alind.gupta@mail.utoronto.ca}}}
\author[1,2]{Julie A. Brill \thanks{\url{julie.brill@sickkids.ca} (Corresponding author)}}
\affil[1]{\small Department of Molecular Genetics, University of Toronto, Toronto, ON M5S 1A8, Canada}
\affil[2]{\small Program in Cell Biology, Hospital for Sick Children, Toronto, ON M5G 1X8, Canada}
\date{}

\begin{document}

\maketitle
\raggedright

\begin{abstract}
  \vspace*{-0.7em}
  Cilia are sensory organelles that are important for human development
  and physiology.
  A large number of genetic disorders affecting cilia are associated with
  mutations in proteins that localize to the transition zone (TZ),
  a structure at the base of cilia required for ciliogenesis and
  regulation of trafficking in and out of the cilium.
  Here, we report that the membrane lipid phosphatidylinositol
  4,5-bisphosphate(\PIP{}) is essential for proper maturation and function
  of TZs in the male \textit{Drosophila melanogaster} germline.
  Reduction of cellular \PIP{} levels by expression of the
  \textit{Salmonella} phosphoinositide phosphatase SigD or mutation of
  the type I phosphatidylinositol phosphate kinase (PIPKI) Skittles (Sktl)
  induces hyperelongation of TZs following their docking at the plasma
  membrane.
  We provide evidence that these hyperelongated TZs are functionally
  defective, and that the Exo84 mutant \textit{onion rings} decouples
  TZ hyperelongation from the role for \PIP{} in cilium-membrane
  tethering.
  Our observations reveals a requirement for \PIP{} at the base of cilia
  in regulating TZ length and function.
\end{abstract}

\section{Introduction}
Cilia are sensory organelles present on almost all cells in the human body
\citep{satir2010primary}.
They function primarily by providing sensory inputs to cells, but can
also function as motile propellers in certain cells
\citep{bloodgood2010sensory}.
Consistent with their pervasiveness and importance in cell signalling,
defects in cilium formation are associated with various genetic disorders
known collectively as ciliopathies, which can display
neurological defects \citep{valente2014primary},
skeletal abnormalities \citep{hammarsjo2017novel, waters2011ciliopathies}
and infertility \citep{inaba2016sperm}.

A large number of ciliopathies are linked to mutations in proteins that
localize to the cilium transition zone (referred to herein as TZ).
The TZ is the proximal-most region of the cilium and
acts as a diffusion barrier that regulates the
bi-directional transport of protein and lipid cargo at the base of the cilium.
The TZ is essential for cilium formation (ciliogenesis) and cilium-associated
signalling.
The conserved TZ protein CEP290, for example, is mutated in at least
five different ciliopathies, and is essential for cilium formation in both humans
and Drosophila \citep{basiri2014migrating}.
Although the protein composition of TZs has been investigated in various
studies ranging from single gene analysis to proteomics,
processes underlying TZ maturation are not as well-studied.

In the Drosophila male germline, nascent TZs first assemble on basal bodies
during early pre-meiotic G2 phase (spermatocytes), anchor directly to the plasma membrane.
This is followed by establishment of cilium-membrane connections and a
ciliary membrane that persists during meiosis \citep{riparbelli2012assembly}
through a poorly understood mechanism
involving microtubule rearrangements \citep{gottardo2013cilium}.
Ciliogenesis begins with the assembly of TZ proteins at the tips of
the nascent basal body.
This is followed by the anchoring of the TZ to the membrane and
establishment of a compartmentalized space bounded by the ciliary membrane
and the TZ.
TZ maturation has been described in
\textit{Paramecium} \citep{aubusson2015transition}
\textit{Caenorrhabditis elegans} \citep{serwas2017centrioles} and
\textit{Drosophila melanogaster} \citep{gottardo2013cilium}
and is most readily observed by an increase in TZ length from nascent to mature.
Possibly, this is similar to the initial steps of TZ assembly and reorganization
in well-studied vertebrate cilia.

Here, we show that the lipid phosphatidylinositol 4,5-bisphosphate (\PIP{})
is essential for proper TZ maturation in developing male germ cells in \textit{D. melanogaster}.
Reduction of cellular \PIP{} by expression of the bacterial PIP phosphatase SigD
or by inactivation of the PIP 5-kinase Skittles (Sktl) that localizes to cilia
induces longer than normal TZs without affecting TZ assembly.
These hyperelongated TZs show hallmarks of aberrant function similar to those
found in previously studied TZ mutants, including loss of cilium-membrane associations.
We also find that the \textit{onion rings} allele of the
ciliopathy-associated \textit{EXOC8} gene encoding the human Exo84
decouples TZ hyperelongation from loss of cilium-membrane contacts.
Our results suggest that the plasma membrane lipid \PIP{} regulates TZ length,
maturation and function, acting to support ciliogenesis.

\section{Results}
\subsection{\PIP{} is essential for transition zone maturation}
To investigate whether reduction of cellular \PIP{} affects ciliogenesis in the
Drosophila male germline,
we used transgenic flies expressing the Salmonella phosphoinositide phosphatase SigD
under $\beta$2-tubulin promoter (referred to herein as \sigd{}),
which is uniquely expressed in spermatocytes
\citep{wei2008depletion, fabian2010phosphatidylinositol}.
We previously showed that expression of this construct
induced male sterility due in part to defects in flagellar biosynthesis \citep{wei2008depletion}.
We examined the localization of fluorescently-labelled centriolar/basal body protein
Ana1 (CEP295 homolog) \citep{goshima2007genes, blachon2009proximal}
and the TZ protein Cep290 \citep{basiri2014migrating}
in wild-type control and \sigd{} spermatocytes.
As shown in Figure 1A, nascent TZs marked with Cep290-GFP assemble normally in \sigd{} cells
but grow to much longer lengths compared to wild-type control cells.
TZ hyperelongation was a highly penetrant phenotype (\textgreater 90\%)
and showed high intra-cyst correlation.
This phenotype was not specific to Cep290;
all TZ markers examined showed hyperelongation, including
acetylated tubulin \citep{gottardo2013cilium},
Chibby \citep{enjolras2012drosophila} and
MKS \citep{slaats2015mks1, vieillard2016transition} proteins (Figure 1).
Hyperelongated TZs persisted through meiosis.
Despite TZ hyperlongation, however, axonemes were able to elongate post-meiosis (Figure 1).
As we showed previously, the ultrastructure of these axonemes was frequently aberrant,
either lacking symmetry completely or containing triplet microtubules instead of doublets
\citep{wei2008depletion}.

\subsection{The type I PIP kinase Skittles localizes to centrioles and regulates TZ length}
Although numerous studies have shown that \PIP{} is the major substrate for SigD
when expressed in eukaryotic cells
\citep{terebiznik2002elimination, zhou2001salmonella, sengupta2013depletion},
SigD can dephosphorylate other PIPs \textit{in vitro}
\citep{norris1998sopb}.
To address whether TZ hyperelongation observed in \sigd{} represented
a physiologically relevant phenotype in response to decreased \PIP{},
we attempted to rescue it by
co-expressing fluorescently-tagged full-length Sktl (Sktl) with SigD
under the same promoter.
We found that Sktl expression was able to suppress TZ elongation in a cilium-autonomous
manner (Figure 2).
We also found that \textit{sktl} clones showed penetrant TZ hyperelongation when
marked with Unc-GFP, a ciliary marker \citep{baker2004mechanosensory}.

Since Sktl expression lead to cilium-autonomous rescue,
we investigated whether Sktl could localize to centrioles or cilia in the Drosophila germline.
Similar to the human PIPKI$\gamma$ isoform \citep{xu2014pipkigamma},
we found that Sktl localizes to basal bodies in the Drosophila male germline.
As shown in Figure 2, Drosophila PIPKIs arose from the recent duplication of
the ancestral PIPKI gene, and are not orthologous to specific vertebrate PIPKI isoforms.
Sktl has diverged more than the paralogous PIP5K59B gene, and seems
to be functionally related to PIPKI$\gamma$ in its roles at cilia.
However, unlike the human PIPKI$\gamma$, which functions to license TZ assembly
by promoting CP110 uncapping from basal bodies \citep{xu2016phosphatidylinositol},
our results suggest that Sktl functions in
regulating TZ length in the Drosophila male germline
but is dispensable for its assembly.
Cp110 is dispensable for cilium formation in Drosophila \citep{franz2013cp110}
and we found its localization to be unaffected in \sigd{} (supplementary figure 1).

@@

\section{Discussion}
Cilia are essential for proper human development, and their disruption
can cause genetic disorders which display severity ranging from congenital
lethality to adult onset.
A large number of ciliopathies are associated with genes that encode for
proteins that function at the cilium transition zone (TZ).
Often, a single gene is linked to multiple ciliopathies with variable phenotypes
and severities.
For example, the conserved TZ protein CEP290 is linked to at least six different
cilium-associated disorders, suggesting that many of these encode for mutant proteins
that are hypomorphic in nature whose function may
be affected by modifier mutations and genetic environment.
Animal models with mild perturbations of TZ function may therefore provide
insight on intermediate phenotypes associated with human disease.
Here, we found that reduced levels of the membrane lipid \PIP{},
which is known to be enriched at the base of cilia,
affects TZ maturation, but not assembly,
leading to hyperelongated TZs that show signs of functional defects, and
may represent one such modifier for TZ function.

In the Drosophila male germline, TZ maturation follows the initial
assembly of TZ proteins on the nascent basal body in the cytoplasm
followed by anchoring at the plasma membrane.
TZ maturation involves microtubule rearrangements and TZ elongation,
which leads to cilium-membrane attachment.
Loss of \PIP{}, a membrane lipid largely at the plasma membrane,
disrupts this process.
It causes excessive lengthening of the TZ,
and disrupts membrane-cilium connections.
Thus, intermediate steps during TZ maturation require \PIP{}.

@@

\section{Methods}
\subsection{Transgenic flies}
Drosophila stocks were cultured on cornmeal molasses agar medium at 25$^{\circ}$C
and 50\% humidity.
Stocks expressing $\beta$\textit{2tubulin}::\textit{Styp}\textbackslash{SigD} (chromosome \textit{3})
and $\beta$\textit{2tub}::YFP-Sktl (chromosome \textit{2})
were described previously \citep{wei2008depletion, fabian2010phosphatidylinositol}.
$\beta$\textit{2tub}::mCherry-Sktl was made as in \citep{wei2008depletion},
and a \textit{P}-element insertion on chromosome \textit{2} was used for rescue using the low-level
expression vector \textit{tv3} \citep{wong2005pip2}.
Ana1-tdTomato (chromosome \textit{2}) and Cep290-GFP (chromosome \textit{3}) were provided
by T. Avidor-Reiss \citep{basiri2014migrating}.
\textit{Sp}/\textit{CyO}; Unc-GFP was originally provided by M. Kernan \citep{baker2004mechanosensory}.
Stocks expressing GFP-tagged Chibby, B9d1, B9d2, Cc2d2a and Mks1 were generously
provided by B. Durand \citep{enjolras2012drosophila, vieillard2016transition}.
The \textit{onr} mutant was described previously \citep{giansanti2015exocyst}.
Stocks for generating \textit{sktl}\textsuperscript{2.3} clones were originally provided by
A. Guichet \citep{gervais2008pip5k}.
\textit{w}\textsuperscript{1118} was used as the wild-type control.

\subsection{Antibodies}
The following primary antibodies were used for immunofluorescence
at the indicated concentrations - 
rabbit anti-Tulp (gift from W. McGinnis \citep{ronshaugen2002structure}), 1:500; 
chicken anti-GFP IgY (abcam) 1:1000;
rat anti-RFP IgG (5F8, ChromoTek), 1:1000;
rabbit anti-Sktl (courtesy of P. Raghu), 1:500;
rabbit anti-\textit{d}Sec6 (courtesy of U. Tepass), 1:500;
mouse anti-acetylated $\alpha$-tubulin 6-11-B (Sigma-Aldrich), 1:1000.
Secondary antibodies were Alexa 488- and Alexa 568-conjugated
anti-mouse, anti-rabbit and anti-chicken
IgG (Molecular Probes) at 1:1000.
DAPI was used to label chromatin at 1:1000.

@@

For Taxol treatments, testes from larvae or pupae expressing
Ana1-tdTomato; Cep290-GFP were
dissected into Shields and Sang M3 medium (Sigma-Aldrich) supplemented
with a predefined
concentration of Taxol and incubated overnight in a humidified sterile
chamber in the dark at room temperature. They were then squashed
in PBS and visualized immediately.

For CellMask staining, cells were spilled from testes in M3 medium onto
a sterilized glass-bottom dish that was pre-treated with sterile polylysine solution
to enable cells to adhere.
CellMask Deep Red (Invitrogen) solution (20 $\mu$g/mL) was added to the medium dropwise
immediately before visualization under a confocal microscope.

For immunochemistry, testes were dissected in PBS,
transferred to a polylysine-coated glass slide in a drop of PBS,
ruptured with a needle, squashed and frozen in liquid nitrogen for 5 minutes.
The slides were transferred to ice-cold methanol for 5-10 minutes for pre-fixation.
For staining with the anti-Sktl antibody, this pre-fixation step
was omitted to preserve cellular membranes.
Samples were fixed in 4\% paraformaldehyde in PBS,
permeabilized and blocked in PBS with 0.1\% Triton-X and 0.3\% bovine
serum albumin and incubated with primary antibodies overnight at 4$^{\circ}$C.
followed by three 5-minute washes with PBS and 1 hour incubation
with secondary antibodies and three 5-minute washes with PBS.
Samples were mounted in Dako (Agilent) and imaged with
a Leica widefield microscope
or Nikon A1R scanning confocal microscope (SickKids imaging facility).

\subsection{Statistical methods}
Statistical analysis and graphing was performed using R.
A Gaussian jitter was applied when plotting
results in Figures 1 and 2 for clearer visualization of trends,
but raw data was used for all analysis.
Statistical tests for ``absence of phenotype'' were computed under a
hypothesis assuming binomial likelihood (i.e. assuming a fixed probability of the
phenotype occurring).
All $t$-tests were unpaired and two-sided.
A significance level of 0.01 was fixed \textit{a priori} for all classical analysis.
All raw data and code for analysis and plotting can be found online
at \url{http://www.github.com/alindgupta/germline-paper/}.

\subsection{Phylogenetic analysis}
Candidate orthologs of Skittles or PIP5K9B were queried
from Inparanoid and FlyBase (version 8.0).
Poorly annotated protein sequences were confirmed
to encode type I phosphatidylinositol phosphate
kinases using reciprocal BLAST search.
Phylogeny.fr (\url{http://www.phylogeny.fr}) was used for
phylogenetic reconstruction with T-Coffee for multiple alignment
and MrBayes for tree construction.
The output was converted to a vector image in Illustrator
and colours were added for the purpose of illustration.

\section{Author contributions}
A.G. and J.A.B. conceived the project.
A.G. performed all the experiments and analysis, and wrote the manuscript.
J.A.B. supervised the project.

\section{Acknowledgements}
We thank Brian Ciruna for his input on the project
and Bénédicte Durand for providing unpublished fly stocks.
This work was supported by a grant from the Canadian Institute for Health Research
(CIHR) to J.A.B.
